An OSGi-based Sensor Network for \\ Environmental Monitoring

### 2009-02-25 docs/icccn2009/paper.tex
Started to work on diagrams
git-svn-id: svn://localhost/netbeams/trunk@315 559edde2-a4d4-44e0-96fc-4035e40d7396

@@

>>>>

Researchers in the geosciences rely on sensor data collected by highly
specialized sensors such as the Seabird or YSI. These sensors are
usually deployed in remote locations that not only make their
maintenance difficult, but also access to their measurements.
Typically the sensors are autonomous in the sense that they can run
for a certain time on battery power and store the measurement data in
internal memory. Only when the sensors are serviced, the measurement
data they have collected since the last servicing are uploaded to a
portable storage device. From there the data can be uploaded to
server. This manual procedure to retrieve sensor data is not only
error prone, but also results in a serious time lag between the time
the sensor performs the measurement and when it becomes available for
further processing. For many applications it would be beneficial to
have near-realtime access to the sensor measurement. Being able to
access data when they become available on the sensor device also
reduces the maintenance overhead.

@@

\begin{figure}
\centering
\epsfig{file=dsp, width=7cm}
\caption{\label{FIG_DSP} Data Sensor Platform (DSP).}
\end{figure}
